Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2019-03-06 awipev-CO2.Rmd
update in script + data tab

@@

###**pH seaFET**
- **2018-08-30**: voltINT + phINT were filtered from 2017-12-14 to 2018-01-08 and bad data were removed from 2018-01-08 to 2018-02-02. pH spectro from 2018-04-16 07:00:00 was fitted with a mean of 4 days of voltINT in order to make the calibration for this 5th period.
- **2018-07-30**: Flag location (location_flag) is added in the script to localize seaFET/durafet discrete samples: flag 1 = at the harbor (not takken in consideration) and flag 0 = in the FB for durafet or on site for seaFET (takken in consideration as "normal" sampling"). See seaFET part.
- **2018-02-02**: Based on Darrell's advices (SeaBird), Philipp implemented the seaFET as: 1h periodic sampling with the following commands: perdival 1h, navg 5, brstsize 1, opermode periodic. 
- **2017-12-29**: "SVL_20171218_010426.dat" from seaFet data was deleted because of bug with its size (0 octect). pH filter was added to "ny_alesund_cc" file for seaFet data (<7.5 and <8.5).

@@

>>>>

[UWO-Ferrybox variables from our sensors](https://docs.google.com/spreadsheets/d/1arKYfUjmg3YrgQ5g9LN_XFwUORyz7nqlKNWq3uYok3U/edit?ts=5c7e1d16#gid=393659093)

[All UWO-Ferrybox data / NearRealTime (NRT) AWI database](https://dashboard.awi.de/data-xxl/overview.jsp)

[Procedure to download NRT data](https://spaces.awi.de/confluence/display/MOS/NRT+data+download+procedures)

@@

###**pH seaFET**
- **2018-08-30**: voltINT + phINT were filtered from 2017-12-14 to 2018-01-08 and bad data were removed from 2018-01-08 to 2018-02-02. pH spectro from 2018-04-16 07:00:00 was fitted with a mean of 4 days of voltINT in order to make the calibration for this 5th period.
- **2018-07-30**: Flag location (location_flag) is added in the script to localize seaFET/durafet discrete samples: flag 1 = at the harbor (not taken in consideration) and flag 0 = in the FB for durafet or on site for seaFET (takken in consideration as "normal" sampling"). See seaFET part.
- **2018-02-02**: Based on Darrell's advices (SeaBird), Philipp implemented the seaFET as: 1h periodic sampling with the following commands: perdival 1h, navg 5, brstsize 1, opermode periodic. 
- **2017-12-29**: "SVL_20171218_010426.dat" from seaFet data was deleted because of bug with its size (0 octect). pH filter was added to "ny_alesund_cc" file for seaFet data (<7.5 and <8.5).

@@

## Villefranche Server informations

- Serveur : awipev-co2 (193.50.85.104)
- 3 comptes: awipev (partagé avec Samir), gattuso, nydata (pour l’envoi des données par P. Fischer).
- Pour se connecter à awipev-co2.obs-vlfr.fr
    - ssh awipev@awipev-co2.obs-vlfr.fr
- Intervention sur le serveur :
    - ssh awipev@awipev-co2.obs-vlfr.fr
    - rebooting Ubuntu server: sudo shutdown -r now
    - to check versions:
        - dpkg -l | grep shiny
        - dpkg -l | grep r-base
    - To update Ubuntu, R and its packages:
        - sudo su
        - apt-get upgrade
    - To restart shiny server: sudo systemctl restart shiny-server
    - update shiny server: follow procedure detailed on the shiny web page

**Data processing**

- Every night at 01:00 (?) two data files ("all sensors" and AT) are sent by ftp to:
    - awipev-co2.obs-vlfr.fr
    - User name: nydata
    - password:
- Every hour a crontab action runs the script ny-alesund/R/ny-alesund_cc.R. This script essentially appends the daily files added each day around 01:00 and cleans the data
- Every night at 03:00 the web page is generated
- Every night at 05:00 the files are copied to gattuso’s iMac

**crontab awipev@awipev-co2.obs-vlfr.fr**

si on veut remplacer intégralement les fichiers de pCloud par ceux de awipev-co2 : ajouter “--delete” à la commande rsync # m h dom mon dow command 
00 */1 * * * cd ; R --vanilla < ny-alesund/R/ny-alesund_cc.R 
00 03 * * * bash web/awipev-co2.sh > web/awipev-co2.log 2>&1 00 05 * * * /usr/bin/rsync -e "ssh -o StrictHostKeyChecking=no" -avh /home/awipev/awipev-co2_web 'gattuso@gattuso.obs-vlfr.fr:/Users/gattuso/pCloud\ Sync/Documents/experiments/exp168_awipev-CO2/fb_awipev-co2_server/' 
00 05 * * * /usr/bin/rsync -e "ssh -o StrictHostKeyChecking=no" -avh /home/awipev/web 'gattuso@gattuso.obs-vlfr.fr:/Users/gattuso/pCloud\ Sync/Documents/experiments/exp168_awipev-CO2/fb_awipev-co2_server/' 
00 05 * * * /usr/bin/rsync -e "ssh -o StrictHostKeyChecking=no" -avh /home/awipev/ny-alesund 'gattuso@gattuso.obs-vlfr.fr:/Users/gattuso/pCloud\ Sync/Documents/experiments/exp168_awipev-CO2/fb_awipev-co2_server/'

**Web page**

- La page web index.html est faite sur awipev@awipev-co2.obs-vlfr.fr
- Création du répertoire web qui contient ce qu’il faut pour générer la page web:
    - AWIPEV-Logo.jpg
    - Discrete_sampling_AWIPEV.csv
    - awipev-CO2_web.Rmd
    - awipev-co2.sh (lancer par bash awipev-co2.sh)
- Accessible https://awipev-co2.obs-vlfr.fr

**On utilise un shell script awipev-co2.sh:**

 #!/bin/bash

 # script de lancement via crontab echo '---------deb awipev-co2.sh -----------'

 # On lance la fabrication du html cd web; R -e 'library("rmarkdown");library("knitr");rmarkdown::render("awipev-CO2_web.Rmd")'; cp awipev-CO2_web.html ../awipev-CO2_web/index.html

echo '---------fin awipev-co2.sh -----------'
